Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-29 paper_v1.Rnw
edited abstract

\begin{abstract}
Research on attrition has a long tradition in the field of education. Large-scale open learning environments prompted a shift away from a monolithic notion of success toward a more nuanced treatment that accounts for diverse motivations. A systematic analysis of predictors of and reported reasons for attrition in 17 massive open online courses suggested time to be a critical obstacle and [other important take-aways from Study 1] (Study 1; $N = XX,XXX$). A follow-up study with online learners who disengaged from the course (Study 2; $ N = 756$) found self-ascribed successful learners to report higher levels of goal striving, feelings of social belonging, and growth mindset. Iterative coding of open responses about challenges learners faced while taking the course reiterated the prevalence of having not enough time (reported by 84\%). A low capacity for volitional control was identified as a large contributor to this issue, besides demands from higher priority obligations. A better understanding of why learners disengage from MOOCs allows for earlier recognition of impending attrition, which enables targeted interventions to help learners achieve their learning goals.
\end{abstract}

>>>>

\begin{abstract}
Research on attrition has a long tradition in the field of education. Large-scale open learning environments prompted a shift away from a monolithic notion of success toward a more nuanced treatment that accounts for the diversity in motivation. A systematic analysis of predictors of and reported reasons for attrition in 17 massive open online courses suggested time to be a critical obstacle and [other important take-aways from Study 1] (Study 1; $N = XX,XXX$). A follow-up study with online learners who disengaged from the course (Study 2; $ N = 756$) found self-ascribed successful learners to report higher levels of goal striving, feelings of social belonging, and growth mindset. Iterative coding of open responses about challenges learners faced while taking the course reiterated the prevalence of having not enough time (reported by 84\%). A low capacity for volitional control was identified as a large contributor to this issue. A better understanding of why learners disengage from MOOCs allows for earlier recognition of impending attrition, which enables targeted interventions to help learners achieve their goals.
\end{abstract}
